\section{\ref{rq:what-is-change-detection} What is change-detection, and what do we want to use it for?}

\todo{This should move to related work}
\subsection{What is change?} \label{what-is-change}

Not many research papers could be found that define the word change. A clear definition of the word \textit{change} was found in a psychology paper by Rensink \cite{rensink2002change}.

\begin{quote}
    "The word change generally refers to a transformation or modification of something over time. As such, this notion presumes a nonchanging substrate on which changes are imposed. More precisely, change is defined here [the paper] as the transformation over time of a well-defined, enduring structure." (Rensink, 2002, p. 248).
\end{quote}

The definition of the word change can be translated to the language of \testar. The "well-defined, enduring structure" refers to the GUI of the system under test, whereas the "transformation over time" refers to the various version of the SUT. The "something" refers to a part of the GUI that can change like: Widget tree, the state or an action. 

Besides defining the word change, Rensink also describes the differences between changes and differences. A change is a transformation of the same 'something', whether a difference lacks the property of the same something. For example, what are the differences between two distinct SUT, or the same SUT but in two distinct environments or Internet Browsers? A limit to the change detection algorithm is that the SUT needs to be executed in the same environment; otherwise, false-positive changes can occur.

This distinction of definitions between change and differences give the first limit to this research paper's proposed change detection algorithm. The change detection algorithm will give the changes of a SUT, between versions, in the same environment since a different environment can influence the model and therefore influence the outcome of the change detection.

\subsection{What change detection?}

toool made by F-secure. collaboration with Pekka GUI Driver. both had features. 

automated masking abstract away know a lot. image comparison. 

GUITAR, something. 

F-secure change detection point it own 
new tool, no paper. 

Change what we are intresing in.

starting state depends on existng data. external changes removed. 

percent of change pixel could indicate .... div > 50\% change then different. 
1 level-> differences on the screen.
2 level-> change in the model (state graph)
3 level-> Form testing, from testing correct and incorrect form
 - hint faker library phone number etc...
 - relationship between 

find values on the new page. releation input value and one of the screen. you input phonenumber. on screen is presented on

metaphorfic testing (relationships). 

Alexander Pretengkro finding state machine. (Aho can connect).

Anomoli detection for change. most change happen on one stap. What if the it stop changes Trent, history change some... change on change detection. 
 
 source: meeting 2 dec with IVVES 